\Title

### 2023-02-09 Grimaldi-etal-BiolCybernetics.tex
methods : A

We want to test our model on a motion detection task on a realistic stream of events. This type of signal, typically recorded by a Dynamic Vision Sensor (DVS), is a good representation of the information and inspired by that sent by the retinal ganglion cells through the optic nerve. With binary events, the visual system is able to capture the dynamics of a natural scene and perform various cognitive tasks in a fast and efficient fashion. To train and test our model, we need to define a dataset for which we control for motion direction and velocity.  First, let's define a trajectory inspired by the biological movements of the eyes. Indeed, these movements allow us to dynamically actuate the center of vision, or gaze, in the field of vision. In animals with a fovea, this is particularly useful as it allows to move the area with the highest density of photoreceptors in the environment, for example at a point of interest. A specific mechanism to do so are called saccades which are rapid eye movements of the eyeball that reposition the center of vision. In humans, these are very frequent (on average $2$ each second~\citep{dandekar_neural_2012}). They are produced very rapidly (about $80~\ms$) and display a whole range of speeds. At a more microscopic scale, the human gaze moves with an incessant drift similar to a Brownian-like trajectory~\citep{poletti_head-eye_2015}. To maintain the full generality of the task, we will define eye movements using a form of random walk~\citep{engbert_integrated_2011}. This approach first defines a finite set of possible 2D motions in polar coordinates. Based on the distribution of biological motions, we simplified it by selecting a set of eye movements as the Cartesian product of % N-V-phi
$8$ linearly spaced motion directions. Next, we define one trajectory of gaze as segments whose duration is drawn from a Poisson distribution with an average block length of $20~\ms$, similarly to a Lévy flight~\citep[p. 289]{mandelbrot_fractal_1982}. Finally, the trajectory is integrated by assuming first that velocities are uniformly and independently sampled from the set of different motion-sets and second that motion is uniform during a time segment. The resulting instances yield trajectories qualitatively similar to those observed for human eye movements (\seeFig{motion_task}-(Left)). 

>>>>

The goal is to test the model in a motion detection task using a realistic data stream. This type of signal is typically recorded by a Dynamic Vision Sensor (DVS). It is a good representation of the information and is inspired by the information sent by retinal ganglion cells through the optic nerve. Binary events allow the visual system to capture the dynamics of the natural scene and carry out different cognitive tasks quickly and effectively. To train and test our model, we need to define a dataset for which we control the direction and speed of motion.  First of all, let's define a trajectory that is inspired by the biological movements of the eyes. Indeed, these movements allow us to dynamically actuate the centre of vision, or gaze, in the visual field. In animals with a fovea, this is particularly useful as it allows the area with the highest density of photoreceptors in the environment to be moved, for example to a point of interest. A specific mechanism for this is called saccades, which are rapid eye movements that reposition the centre of vision. In humans, saccades are very frequent (on average $2 per second~\citep{dandekar_neural_2012}). They are generated very quickly (about $80~\ms$) and they have a whole range of speeds. On a more microscopic scale, the human gaze moves with a continuous drift similar to a Brownian trajectory~\citep{poletti_head-eye_2015}. In order to maintain the full generality of the task, we will define eye movements using a form of random walk~\citep{engbert_integrated_2011}. 
This approach first defines a finite set of possible 2D movements in polar coordinates. Based on the distribution of biological motions, we simplified it by selecting a set of eye movements as the Cartesian product of $8$ linearly spaced motion directions. Next, we define a gaze trajectory as segments whose duration is drawn from a Poisson distribution with a mean block length of $20~\ms$, similar to a Lévy flight~\citep[p. 289]{mandelbrot_fractal_1982}. Finally, the trajectory is integrated, assuming first that the velocities are sampled uniformly and independently from the set of different motion sets, and second that the motion is uniform during a time segment. The resulting instances yield trajectories that are qualitatively similar to those observed for human eye movements (\seeFig{motion_task}-(left)).
